\section{Experiments}
\label{sec:experiments}

\emph{This section is a skeleton. The benchmark is methodologically complete; the
results below are populated from the first full evaluation run. Each subsection
states the table or figure it will contain, the artifact that fills it, and the
script that generates it. No numbers are reported until the run exists; every cell
is a bracketed placeholder.}

\subsection{Setup}

The configured launch roster is eleven models: ten current models across
frontier-closed, efficient-closed, and open-weight tiers, plus one legacy
cross-generation anchor (GPT-4.1), all configured in
\texttt{eval/config.py} (verified against live provider sources at configuration
time and pinned to dated snapshots where the provider publishes one). All models
are evaluated on both domains over the full public corpus, three reliability runs
each, scored by the three-judge panel. Token prices are dated per run. The
do-nothing probe is run separately as the anti-gaming sanity check. Source for all
of this subsection: \texttt{pre\_registration.json} and
\texttt{run\_manifest.json}.

\subsection{Leaderboard}

\textbf{Table~\ref{tab:leaderboard} (planned):} per-model CLEAR composite with
95\% interval and rank band, efficacy with interval, \$/task, reliability (pass@3),
and latency, sorted by CLEAR descending, with the per-domain breakdown beneath.
\emph{Fills from:} \texttt{leaderboard.json} (\texttt{models[]} with
\texttt{clear\_score}, \texttt{clear\_score\_ci}, \texttt{rank\_band},
\texttt{efficacy}, \texttt{efficacy\_ci}, \texttt{cost}, \texttt{reliability},
\texttt{latency}) and \texttt{latest.csv}. \emph{Generated by:}
\texttt{scripts/aggregate\_results.py}.

\begin{table}[h]
\centering
\caption{COT Bench v1 leaderboard (placeholder). Rank bands group models whose
CLEAR intervals overlap; within a band, ordering is not statistically
distinguishable.}
\label{tab:leaderboard}
\begin{tabular}{clccccc}
\toprule
\textbf{Band} & \textbf{Model} & \textbf{CLEAR (95\% CI)} & \textbf{Efficacy} & \textbf{\$/task} & \textbf{Reliability} & \textbf{Latency} \\
\midrule
\TODO{1} & \TODO{model} & \TODO{x [lo, hi]} & \TODO{x} & \TODO{x} & \TODO{x} & \TODO{x} \\
\TODO{$\vdots$} & & & & & & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Judge versus deterministic state check: the divergence analysis}

\textbf{Figure (planned):} per-model scatter of judge-consensus efficacy (task +
tool components) against the deterministic state score, with the diagonal marked.
Points far below the diagonal are models the judges credit more than the world
state warrants; the systematic direction of that gap is a finding about the limits
of judge-only evaluation. \emph{Fills from:} per-row \texttt{task\_completion} /
\texttt{tool\_selection} consensus and \texttt{state\_score} in the results parquet
and the per-evaluation artifacts. \emph{Generated by:} a plotting script over the
results parquet (see \texttt{paper/figures/README.md}).

\subsection{Same-lab and per-judge deltas}

\textbf{Table/figure (planned):} for every contestant and every judge, the judge's
mean minus the consensus, with the same-lab Anthropic pairing highlighted and the
open-judges-only recomputation shown for the Claude contestants. A consistent
pattern where a judge rates its own-lab model above consensus is the headline
candidate; the absence of one is equally publishable. \emph{Fills from:}
\texttt{judge\_deltas} and \texttt{same\_lab\_check} per model in
\texttt{leaderboard.json}. \emph{Generated by:}
\texttt{compute\_judge\_deltas} / \texttt{compute\_same\_lab\_check} in
\texttt{scripts/aggregate\_results.py}.

\subsection{$\text{pass}^k$ reliability decay}

\textbf{Figure (planned):} $\text{pass}^k$ versus $k$ for $k \in \{1,2,3\}$ per
model, showing how reliability collapses as the all-succeed horizon lengthens. This
is the autonomy-horizon view. \emph{Fills from:}
\texttt{reliability\_pass\_hat\_k} per model in \texttt{leaderboard.json}.
\emph{Generated by:} \texttt{compute\_pass\_hat\_k\_by\_model} in
\texttt{scripts/aggregate\_results.py}.

\subsection{Cost-performance Pareto}

\textbf{Figure (planned):} \$/task on the x-axis against efficacy (or reliability)
on the y-axis, with the Pareto frontier marked, to surface the cheapest
production-reliable choice. \emph{Fills from:} per-model \texttt{cost},
\texttt{efficacy}, \texttt{reliability} in \texttt{leaderboard.json}.
\emph{Generated by:} a plotting script over \texttt{leaderboard.json}.

\subsection{Public-versus-holdout gap}

\textbf{Table (planned):} per-model public score, holdout score, and gap, the
overfitting tripwire. Only aggregates are shown; no holdout scenario detail is
published. \emph{Fills from:} the per-model holdout aggregates in
\texttt{leaderboard.json} (private run only). \emph{Generated by:}
\texttt{scripts/aggregate\_results.py} with a holdout directory configured.

\subsection{Inter-judge reliability and length bias}

\textbf{Table (planned):} Krippendorff's $\alpha$ overall and per dimension, plus
the length-bias regression (slope, $t$, $R^2$, significance flag) per judge
dimension. \emph{Fills from:} \texttt{judge\_alpha} and \texttt{length\_bias} in
\texttt{leaderboard.json}. \emph{Generated by:} \texttt{compute\_judge\_alpha} and
\texttt{compute\_length\_bias} in \texttt{scripts/aggregate\_results.py}.

\subsection{Anti-gaming probe}

\textbf{Result (planned, one line):} the do-nothing agent is expected to collapse
to near the composite floor, with the deterministic state component reported at
0.0 on mutation-expecting scenarios and the judge components at their floor, as
direct evidence the scores reflect verified work; \TODO{report the observed
null-agent efficacy}. \emph{Fills from:} a \texttt{--include-null-agent} run's artifacts.

\subsection{Calibration}

\textbf{Result (planned, deferred):} human-versus-judge $\alpha$, mean absolute
difference, and Pearson correlation against the consensus and each individual
judge, from the blind labeling workbook. Runs after the rehearsal run produces
transcripts; needs human hours, not API spend. \emph{Generated by:}
\texttt{scripts/calibration.py}.
