Most agentic benchmarks score a single LLM judge against a transcript, which makes
the resulting leaderboard only as trustworthy as that judge and as gameable as its
preferences. COT Bench evaluates multi-turn, tool-calling agents on two production
domains (banking and customer success) with a scoring design built to reduce that
dependence. Efficacy is hybrid: two LLM-judge dimensions (task completion and tool
selection) plus a deterministic, judge-independent state check that verifies
whether the agent actually changed the world the way the task required, scored
against a per-scenario ground-truth world with no model in the loop. The judge
component is a three-model panel drawn from three different labs, none of which is
under test, with consensus taken as the median and inter-judge reliability reported
as Krippendorff's $\alpha$. Every individual judge score is published, including a
per-judge-versus-consensus delta that turns any judge's favoritism (including the
one same-lab pairing) into a measured number rather than a hidden risk. Beyond
efficacy, the benchmark reports cost, reliability, and latency in a CLEAR-aligned
composite; reliability is measured with $\text{pass}^k$ (all-$k$-succeed), the
sharper tau-bench reliability construct. The board publishes a 95\% nonparametric
bootstrap confidence interval on every headline number, clusters statistically
indistinguishable models into rank bands, refuses to publish below a minimum
scenario count, and fits a length-bias regression to test whether longer outputs
earn higher judge scores. Governance is explicit: runs are pre-registered before
the first model call, judge versions are pinned and the actually-served model is
recorded, published runs are never silently retracted, and a hash-pinned private
holdout measures the public-versus-holdout overfitting gap. A do-nothing agent is
run as a standing anti-gaming probe. The public corpus is 92 scenarios
(49 banking, 43 customer success), all carrying ground-truth worlds.
On the configured launch roster of eleven models, [headline finding pending first run --
candidate framings: per-judge same-lab delta of \TODO{X}; cost-reliability Pareto
showing a \TODO{X}$\times$ cheaper model at comparable reliability;
$\text{pass}^1 \rightarrow \text{pass}^3$ decay of \TODO{X}; public-vs-holdout gap
of \TODO{X}]. All code, scenarios, rubrics, and per-run artifacts are open
(Apache~2.0).
